\begin{frame}{Questions to Keep in Mind}
  \begin{itemize}
\item What problem are we trying to solve?
\item Why do we want to solve it?
\item \textbf{What are some notable results in our work?}
%\item <+-> ``The Surprising Power of Constant Depth Algebraic Proofs'' has 37 pages and on ECCC
%\item <+-> I really want to thank the original speaker 
\end{itemize}
\end{frame}

\begin{frame}{Notable Results}
  \begin{itemize}
    \item In our paper, we aim to classify the $K$ and $d$ for which we can
  achieve $n^{1+o(1)}$ running times. We also aim to classify the $K$
  and $d$ for which you cannot achieve a running time better than
  $n^{2-o(1)}$.
    
  \item Here are two of our many results:
  \end{itemize}
\end{frame}

\begin{frame}{Notable Results}
  \begin{enumerate}
    \item <+-> There exist almost-linear time algorithms for finding
      {\color{darkblue}spectral sparsifiers} of a $K-graph$ in high dimension ($\theta(\log n)$) for any
      $K(x, y) = f(\|x-y\|_2)$ where $f$ is a polynomial with positive
      coefficients.
    \item <+-> {\color{red}Matrix-vector multiplication} and
      {\color{darkgreen}solving Laplacian
      systems} must take $n^{2-o(1)}$ time in $\theta(\log n)$ dimension,
      for any function $K$ that is not tightly approximated by any
      polynomial, assuming the Strong Exponential Time Hypothesis
      (SETH). 
      \begin{enumerate}
        \item If $K$ is a polynomial, you can do these tasks quickly.
        \item The functions $K(x,y) = \frac{1}{\|x-y\|_2^2}$ or
          $K(x,y)=e^{-\|x-y\|_2}$ are not tightly approximated by any
          polynomial.
      \end{enumerate}
  \end{enumerate}
\end{frame}

