% \begin{frame}{What is a criterion for when points embed into
%   Euclidean Distance?} 
%   \begin{itemize}[<+->]
%   \item  A distance $d$ on an $n$ point set is a Euclidean distance if and only
%   if the matrix $D$ with:
% 
%  \[ D_{ij} = d(i, j)^2 \]
% 
%  has the property that $x^T D x \leq 0$ for all $x \bot 1$.
%   \end{itemize}
% \end{frame}

\begin{frame}{What is a criterion for when points embed into
  \textbf{Squared}
  Euclidean Distance?} 
  \begin{itemize}[<+->]
  \item  A distance $d$ on a set $\{x_1, \ldots x_n\}$ is a \textbf{squared} Euclidean distance if and only
  if the matrix $D$ with:

 \[ D_{ij} = d(x_i, x_j) \]
 \pause
 has the property that $x^T D x \leq 0$ for all $x \bot 1$ [Schoenberg
 '35].
 \pause
 \item A matrix with this property is called a \textbf{negative type}
 matrix. (Classical)
  \item Here, we assume $d(x,x) = 0$ and $d(x,y) = d(y,x)$. We do not
  assume metric property.
  \item But how can we test for this???
  \end{itemize}
\end{frame}
% \begin{frame}{Example} 
%   \begin{itemize}[<+->]
%   \item Consider a 2 point set $\{x, y\}$ where $d(x,y) = \pi$.
%   \item 
%   $ \begin{pmatrix} 
%   0 & \pi \\
%   \pi & 0
%   \end{pmatrix}
%   $
%   has the property that $x^T D x  \leq 0$ for $x \perp \overrightarrow{1}$.
%   \item Therefore, $d$ is a squared Euclidean distance.
%   \end{itemize}
% \end{frame}
% \begin{frame}{Example} 
%   \begin{itemize}[<+->]
%   \item Consider the 3 points $(0, 0), (0, 1), (1, 1)$.
%   \item The Euclidean distances are $1, 1, \sqrt{2}$.
%   \item The squared Euclidean distances are $1, 1, 2$.
%   \item Therefore (by our theorem):
%     \pause
%      \[D = 
%   \begin{pmatrix} 
%   0 & 1 & 2 \\
%   1 & 0 & 1 \\
%   2 & 1 & 0
%   \end{pmatrix}
%   \]
%   \pause
%   has the property that $x^T D x  \leq 0$ for $x \perp \overrightarrow{1}$.
%   \end{itemize}
% \end{frame}


\begin{frame}{A Sufficient Criterion for Negative Type Matrices}
  \begin{itemize}[<+->]
  \item Let $D$ be a symmetric matrix.
  \item Suppose $D$ has eigenvector $\overrightarrow{1}$, and all other
  eigenvectors have negative eigenvalue.
  \item Show that $D$ is negative type: $x^T D x \leq 0$
      for all $x \perp 1$.
  \end{itemize}
\end{frame}

 \begin{frame}{Example} 
   \begin{itemize}[<+->]
   \item Let 
   $ D = \begin{pmatrix} 
   0 & 1 \\
   1 & 0
   \end{pmatrix}.$
   This has eigenvector $\overrightarrow{1}$, and all other eigenvectors $(1,
       -1)$ have negative eigenvalue.
   \item Therefore, it of negative type, and the associated distance is
   a squared Euclidean distance.
   \end{itemize}
 \end{frame}

 \begin{frame}{Exercise} 
   \begin{itemize}[<+->]
   \item Show that
   $ D = \begin{pmatrix} 
   0 & 1 & 1\\
   1 & 0 & 1\\
   1 & 1 & 0\\
   \end{pmatrix}.$
   is a negative type matrix!
   \end{itemize}
 \end{frame}
\begin{frame}{A Sufficient Criterion for Showing a Distance is Squared
  Euclidean}

Let $d$ be a distance on set $x_1, \ldots x_n$, such that the matrix
$D$ with $D_{ij} = d(x_i, x_j)$ satisfies:
  \begin{itemize}
  \item $D$ has $\one$ as an eigenvector.
  \item  All other eigenvalues of $D$ are negative.
  \end{itemize}
  Then $D_{ij}$ embeds into squared Euclidean distance!
\end{frame}


